Supplementary information for Marine species do not need visas: the transboundary nature of the world’s exploited marine species

### 2020-08-05 Scripts/supplements.Rmd
created supplements file

```{r Call_Sup_1, eval = T, fig.width=5, fig.height=3, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon."}

@@

```{r Call_Sup_4, eval = T, fig.width=6, fig.height=4, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis"}

@@

read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
  clean_names() %>% 
  filter(sub_region != "Other") %>% 
  arrange(sub_region) %>% 
  rename("UN sub region" = sub_region,
         "Area of EEZs (Km^2)" = size_entity_sum) %>% 
  kable("latex",
        booktabs = T,
        caption= "Size of all the EEZs in each sub region determined by the United Nations")

@@

```{r Call_SupT_2, eval = T, echo = F, fig.pos= "H"}

read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
  kable("latex",
        booktabs = T,
        caption= "Average number of transboundary and discrete species per EEZ for each catch trend")

>>>>

```{r Call_Sup_1, eval = T, fig.width = 9, fig.height = 7, echo=FALSE, fig.pos= "H", fig.cap="Number of transboundary species per EEZ and their contributions to countries’ EEZ catch. The number of species is displayed in the EEZ while catch (in thousand tons) is displayed in the land polygon."}

@@

```{r Call_Sup_4, eval = T, fig.width=6, fig.height=9, echo=FALSE, fig.pos= "H", fig.cap=" Histogram of number of transboundary species using different Area Index threshold values. The darker histogram represents the threshold (25%) used in the present analysis"}

@@

read.csv("~/GitHub/FishForVisa/Tables/Table_S1.csv") %>% 
  clean_names() %>% 
  filter(sub_region != "Other") %>% 
  arrange(sub_region) %>% 
  rename("UN sub region" = sub_region,
         "Area of EEZs (Km^2)" = size_entity_sum) %>% 
  kable("latex",
        booktabs = T,
        caption= "Size of all the EEZs in each sub region determined by the United Nations") %>% 
  kable_styling(full_width = T)

@@

```{r Call_SupT_2, eval = T, echo = F, fig.pos= "H", message = F, warning = F}

read.csv("~/GitHub/FishForVisa/Tables/Table_S2.csv") %>% 
  clean_names() %>% 
  rename(
    Category = category,
    "Mean (s.d.) Transboundary" = mean_shared,
    "Mean (s.d.) Discrete" = mean_discrete) %>% 
  kable("latex",
        booktabs = T,
        caption= "Average (standard deviation) number of transboundary and discrete species per EEZ for each catch trend category")
